The necessity of hypermedia RDF and an approach to achieve it

### 2012-03-01 eswc-2012/workshop2.tex
more updates from the old paper
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@135 43ef1190-90fd-4dd7-a769-d0121f02b80e

>>>>

In a read-only situation, the HATEOAS constraint requires that the
application can navigate from one resources to another using the
hypermedia links in the present resource \emph{only}, it should not
require any out-of-band information to do so. Thus, a RESTful protocol
should not require prior knowledge of a URI structure, but one may
define the protocol in terms of URI structure as long as the same
information can be gleened from the resources. Nor does it require
that all resources can be reached from any other resource. As such,
the constraint is not very strict, one could argue that as long as
there are some links, the protocol satisfies the HATEOAS constraint.

Since RDF is built on URIs, many of which can be dereferenced to
obtain further links, it lends itself well to RESTful protocols, but
it is debateable whether a protocol can be said to be RESTful if the
links doesn't enable any useful interactions. Importantly, if there is
to be such a thing as a RESTful read-write Semantic Web protocol,
there must be something in the RDF itself that can be used by
practical applications to write data. Therefore, whether the HATEOAS
constraint is satisfied must be judged on the basis of the practical
applications the protocol enables.
